Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/semantics.tex
pass over the overview

>>>>

\fbox{\parbox{5in}{
\paragraph{Blend.}
the
function \texttt{qs} does \emph{not} depend on the rank \texttt{k};
for example, the list is partitioned before \texttt{k} is ever
used. Moreover, while the recursive calls to \texttt{qSelect} are
guarded by a comparison to \texttt{k}, \texttt{k} does not determine
the arguments to those recursive calls---it only determines which call
is made. Thus, if we are willing to change the evaluation order of the
language (and evaluate under the \texttt{case} statement), it should
be possible to force \emph{all} the computations involving \texttt{l}
to be performed before \emph{any} of the computations involving
\texttt{k}.

The \texttt{case} expression in \texttt{qSelect} depends on \texttt{k}, whose
type $\fut\rmint$ indicates that it is only available to second-stage
computations. Since \texttt{qsStaged} itself produces a $\fut\rmint$, the
remainder of the function is second-stage code.

The $\next$ wraps a second-stage expression of type $\rmint$ (the \texttt{case}
expression) as a first-stage expression of type $\fut\rmint$ (the result 
of \texttt{qsStaged}). Inside the \texttt{LT} and \texttt{GT} branches, the
$\prev$ unwraps first-stage $\fut\rmint$s (the results of the recursive calls
to \texttt{qsStaged}) as second-stage $\rmint$s. In the \texttt{EQ} branch,
$\pause$ promotes a first-stage $\rmint$ (the head of \texttt{l}) directly to a
second-stage $\rmint$.

}}
